VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-19 snapshot_system/paper_arch.tex
re

\subsection{Per Node Software Components} 
%\begin{figure}[htbp]
\begin{figure}[htbp]
    \centering
    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
    \includegraphics[width=2.2in]{images/socc_arch_cluster}
    \caption{Data flow during snapshot backup}
    \label{fig:arch_vm}
\end{figure}
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

\subsection{A VM-centric Snapshot Store}
\label{sect:store}
%\begin{figure}[htbp]
\begin{figure}[htbp]
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=2.2in]{images/sstore_arch}
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

PDS data are re-calculated periodically, but 
the total data size is small.  When
a new PDS data  set is computed, the in-memory PDS index is replaced, but 
the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
The old data are not removed because they can still be referenced by the existing snapshots. 
A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).

@@

Three API calls are supported for data backup:
%\begin{itemize}

%\item
\noindent\textbf{Append()}. 
For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
This operation  may only be used during PDS recalculation.
For non-PDS data, this call places a chunk into 
the snapshot store and returns a reference to be stored in the recipe of a snapshot. 
The write requests to append chunks to a VM store are accumulated at the client side. 
When the number of write requests reaches a fixed group size, the client compresses
the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
appends the header and data  to the corresponding VM file.
A new container  index entry is also created for each chunk group and is written to the corresponding
container index file.

%\item
\noindent\textbf{Get()}.
Fetching PDS data is straightforward since each reference contains 
the file offset, and the size of a PDS chunk is available from a segment recipe.
We also maintain a small data cache for the PDS data service to speedup common data fetching.
To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client 
first loads the
corresponding VM's container index file specified by the container ID, then searches the chunk
groups  using their  chunk ID coverage.
After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
specified by the chunk ID. 
Finally, the client updates its internal chunk cache with the newly loaded content to 
anticipate future sequential reads.

%\item
\noindent\textbf{Delete()}.
Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user (the overall deletion strategy was discussed in detail in Section~\ref{sect:delete}).
When deletion requests are issued for a specific container,
those requests are simply recorded into the  container's deletion log initially and thus  a lazy
deletion strategy is exercised.
Once local chunk IDs appear in
the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
will only be used if they also exist in other snapshots.
Periodically, the snapshot  store identifies those containers with an excessive
number of deletion requests to  compact and  reclaim the corresponding disk space. 
During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
found in the deletion log to the new container, and creating new chunk groups and indices. 
Every local chunk ID however is directly copied rather than re-generated. This
process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
As a result, all data references stored 
in recipes are permanent and stable, and the data reading process
is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
depend directly on physical storage locations, which simplifies data migration.
%\end{itemize}

>>>>

\subsection{Per Node Software Components} 
%\begin{figure}[htbp]
\begin{figure}[htbp]
\vspace{1em}
    \centering
    %\includegraphics[width=2.75in]{images/socc_arch_cluster}
    \includegraphics[width=3in]{images/socc_arch_cluster}
%\vspace{1em}
    \caption{Data flow during snapshot backup}
    \label{fig:arch_vm}
\end{figure}
As depicted in Figure~\ref{fig:arch_vm}, 
there are four key service components running on each cluster
node  for supporting backup and deduplication: 
1) a virtual block device driver, 2) a snapshot deduplication agent,
3) a snapshot store client to store  and access snapshot data,
and 4)  a PDS client to support PDS metadata access.

@@

\subsection{A VM-centric Snapshot Store}
\label{sect:store}

%\begin{figure}[htbp]
\begin{figure}[htbp]
\vspace{1em}
  \centering
%  \includegraphics[width=2.75in]{images/sstore_arch}
  \includegraphics[width=3in]{images/sstore_arch}
%\vspace{1em}
  \centering
  \caption{VM snapshot store data structures}
  \label{fig:as_arch}
\end{figure}

@@

PDS data are re-calculated periodically in an offline manner, but 
the total data size is small.  When
a new PDS data  set is computed, the in-memory PDS index is replaced, but 
the PDS file on the disk appends the  new PDS data identified and the growth of this file is very slow. 
The old data are not removed because they can still be referenced by the existing snapshots. 
A periodic cleanup is conducted  to remove unused PDS chunks (e.g. every few months).

@@

Three API calls are supported for data backup:
\begin{itemize}

\item
\noindent\textbf{Append()}. 
For PDS data, the chunk is appended to the end of the PDS file and the offset is returned as the  reference.
This operation  may only be used during PDS recalculation.
For non-PDS data, this call places a chunk into 
the snapshot store and returns a reference to be stored in the recipe of a snapshot. 
The write requests to append chunks to a VM store are accumulated at the client side. 
When the number of write requests reaches a fixed group size, the client compresses
the accumulated   chunk group, adds a chunk group index  to the beginning of the group, and then
appends the header and data  to the corresponding VM file.
A new container  index entry is also created for each chunk group and is written to the corresponding
container index file.

\item
\noindent\textbf{Get()}.
Fetching PDS data is straightforward since each reference contains 
the file offset, and the size of a PDS chunk is available from a segment recipe.
We also maintain a small data cache for the PDS data service to speedup common data fetching.
To read a non-PDS chunk using its reference with container ID and local chunk ID,  the snapshot store client 
first loads the
corresponding VM's container index file specified by the container ID, then searches the chunk
groups  using their  chunk ID coverage.
After that, it reads the identified chunk group from DFS, decompresses it, and seeks to the exact chunk data 
specified by the chunk ID. 
Finally, the client updates its internal chunk cache with the newly loaded content to 
anticipate future sequential reads.

\item
\noindent\textbf{Delete()}.
Chunk deletion occurs when a snapshot expires or gets deleted explicitly by a user. 
%(the overall deletion strategy was discussed in detail in Section~\ref{sect:delete}).
When deletion requests are issued for a specific container,
those requests are simply recorded into the  container's deletion log initially and thus  a lazy
deletion strategy is exercised.
Once local chunk IDs appear in
the deletion log, they will not be referenced by any future snapshot and can be safely deleted when needed. 
This is ensured because we only dedup against the direct parent of a snapshot, so the deleted snapshot's blocks
will only be used if they also exist in other snapshots.
Periodically, the snapshot  store identifies those containers with an excessive
number of deletion requests to  compact and  reclaim the corresponding disk space. 
During compaction, the snapshot store creates a new container (with the same container ID) to replace the 
existing one. This is done by sequentially scanning the old container, copying all the chunks that are not 
found in the deletion log to the new container, and creating new chunk groups and indices. 
Every local chunk ID however is directly copied rather than re-generated. This
process leaves holes in the chunk ID values, but preserves the order and IDs of chunks.
As a result, all data references stored 
in recipes are permanent and stable, and the data reading process
is as efficient as before. Maintaining the stability of chunk IDs also ensures that recipes do not
depend directly on physical storage locations, which simplifies data migration.
\end{itemize}

### 2014-07-19 snapshot_system/paper_background.tex
re

Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
is still extensive for a shared cloud cluster.  
For example, in the experiment discussed in Section~\ref{sect:evaldedup}, 
the raw snapshot data has a size of 1,000TB on 100 physical machines that host VMs,
cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
still needs several gigabytes of memory per machine. This can impact other primary cloud services sharing the same
computing resource. Our objective is to have an approximation scheme 
which uses no more than a few hundred megabytes of memory during normal operation.
The desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
Our proposed scheme achieves 85K:1
and this ratio is about the same as the number of machines increases.

Index sampling with a prefetch cache  is proposed in
in~\cite{Guo2011} for efficient single-machine deduplication. 
This scheme uses 25GB memory per 500TB of raw data
and thus the raw data to memory ratio is 20K:1. Our scheme proposed in this paper 
uses three times less memory and we have not incorporated this index 
sampling technique because its extension for
for a distributed architecture is difficult.  To use a distributed memory version 
of the sampled index, every deduplication
request may access a remote machine for index lookup and the overall overhead 
of access latency for all requests can be significant.

@@

While deduplication reduces storage cost, it creates an artificial data dependence among VMs: when a shared data chunk
is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
This issue is identified in ~\cite{Reliability06} which proposes to use more replication for data shared by more files,
and we will adopt this idea.
When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
 typically use smaller chunk sizes (e.g. 4K bytes).
Thus we need to consider the size gap between file system blocks and chunks  in adding more replications for popular chunks.

Another disadvantage of cross-VM sharing is that it complicates
snapshot deletion, which is the garbage collection in VM environment
that occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage collection could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which is still too big to be hold anywhere in a converged architecture.

@@

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, which occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly dedupable which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which is still too big to be hold anywhere in a converged architecture.

>>>>

Even with these optimization and approximation techniques, resource usage such as memory  for deduplication
is still extensive for a shared cloud cluster.  
For example, in the experiments discussed in Section~\ref{sect:evaldedup}, 
the raw snapshot data has a size of 1,000TB on 100 physical machines that host VMs,
cross-machine fingerprint comparison using Bloom filter and approximated routing~\cite{bottleneck08,Dong2011} 
still needs several gigabytes of memory per machine. This can impact other primary cloud services sharing the same
computing resource. Our objective is to have an approximation scheme 
which uses no more than a few hundred megabytes of memory during normal operation.
Thus the  desired ratio of raw data to memory ratio is from 100K:1 to 30K:1.
Our proposed scheme achieves 85K:1
and this ratio is about the same as the number of machines increases.

Index sampling with a prefetch cache  is proposed 
in~\cite{Guo2011} for efficient single-machine deduplication. 
This scheme uses 25GB memory per 500TB of raw data
and thus the raw data to memory ratio is 20K:1. The scheme proposed in this paper 
uses three times less memory. We have not incorporated this index 
sampling technique because it is difficult to extend 
for a distributed architecture.  To use a distributed memory version 
of the sampled index, every deduplication
request may access a remote machine for index lookup and the overall overhead 
of access latency for all requests is significant.

@@

While deduplication reduces storage cost, it creates an artificial data dependence among VMs: when a shared data chunk
is lost in the storage, all VMs that refer such chunks after deduplication face a data loss.
The work in ~\cite{Reliability06} identifies such an issue in file systems 
and uses more replication for data shared by more files,
and we will adopt this idea.
When the backup storage is implemented using a distributed file system such as Hadoop and Google file system~\cite{googlefs03},  
the file system block  size is often chosen to be large (e.g. 64MB). On the other hand, 
deduplication implementations~\cite{Guo2011,extreme_binning09,bottleneck08,Jin2009,Dong2011}
 typically use smaller chunk sizes (e.g. 4K bytes).
Thus we need to address  the size gap between file system blocks and chunks.  
%in adding more replications for popular chunks.

%Another disadvantage of cross-VM sharing is that it complicates
Snapshot deletion 
%which is the garbage collection in VM environment
occurs frequently because snapshots expire regularly
and reference counting is required to identify chunks that are no loner used.
%Several well developed garbage collection methods do not apply to the
%converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is effective for deletion by tracking
the dependencies from data containers to metadata groups, but still it carries
a significant cost in a cloud cluster. This is because any data chunk can still be
used by a large number of VMs, and there are multiple rounds of extensive I/O involved
to scan through the meta data of snapshots to check if a chunk is referenced or not.
As the number of machines increases, the I/O cost becomes more expensive.
% and  we show  such that only a subset of
%metadata needs to be scanned in order to reclaim the garbage in any given data container.
%However, data in VM environment tend to be highly dedupable which means
%such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
% especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scanning of all data hashes before any 
garbage collection could begin, which limits its application to an offline batch process. 
In addition, it requires a centralized location
to store the hashing result which is still too big to hold in a converged architecture.

@@

Another disadvantage of cross-VM sharing is that it complicates 
snapshot deletion, which occurs frequently because snapshots expire regularly.
Several well developed garbage collection methods do not apply to the
converged virtualized architecture due to various environment and resource limitations:
Grouped mark-and-sweep~\cite{Guo2011} is an effective approach by tracking
the dependencies from data containers to metadata groups, such that only a subset of
metadata needs to be scanned in order to reclaim the garbage in any given data container.
However, data in VM environment tend to be highly redundant which means
such dependency could be extensive, therefore scanning a large subset of metadata still carries a significant cost,
 especially in a distributed setting.
Perfect hashing~\cite{Fabiano2013} provides a very memory efficient way to represent a large set of
hashes in a compact form, however, it still requires the scan of all data hashes before any garbage could begin,
which limits its application to only offline batch garbage collection. In addition, it requires a centralized location
to store the hashing result which is still too big to be hold anywhere in a converged architecture.

### 2014-07-19 snapshot_system/paper_dedup.tex
re

% {\it [Need to find a place to put these numbers in: Total number of chunks 
% in 350 snapshots: 1,546,635,485. 
% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
The observation that motivates us to use the PDS
is that for those chunks that appear in different VMs, the top $k$ most popular items
dominate the distribution.  
Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
We define chunk popularity as the number of unique copies of the chunk in the data-store,
i.e., the number of copies of the chunk after local deduplication.
%the distribution of chunk popularity~\cite{WeiZhangIEEE} 
%based on a production data trace from Alibaba with over 2500 VMs.
The distribution from this figure is Zipf-like. 
Let  $\sigma$ denote as the percentage of unique data chunks belonging to PDS and 
from the evaluation in Section~\ref{sect:evaluation}, we find that
$\sigma$ with about  2\% can deliver a fairly competitive deduplication efficiency.
%$\sigma$ with about  range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
%For example,
%with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
%data can be eliminated by fingerprint lookup in PDS index.

%when restricting fingerprint comparison within a VM uses
%only a small amount of resource. 
%ehat the local deduplication has removed most of the duplicates.
%There are fewer deduplication opportunities across VMs while the memory and network
%consumption for global comparison is more expensive.
%Thus our approximation is that the global cross-VM fingerprint comparison only searches for the top $k$
%most popular items. 
PDS  can be computed periodically, e.g., on a monthly basis.
%Once the popularity of all data chunks is collected, the system only maintains the top $k$
%most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
%These top chunks are shared among multiple VMs and  since $\sigma$ is relatively small, 
%we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
%analytic design guidance. 
% Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
% The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
% We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
% $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.

Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $100-\sigma$ percentage
(e.g. 98\% with $\sigma=2\%$)
and the searchable fingerprint space  becomes very small under the popularity constraint.  
The fingerprint-guided distributed mapping in ~\cite{extreme_binning09,Dong2011} narrows
the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
used for the entire deduplication. 
%In comparison we only focus on top popular chunks among VMs and this
%significantly reduces the total amount of  searchable fingerprints.

\comments{
We have not adopted the index sampling in \cite{Guo2011} because its extension for
for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication 
request may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.
}
\item 
\textbf{VM-specific duplicate search optimization} --
While cross-VM deduplication is simplified, we intend to optimize the VM-specific deduplication 
as much as possible under a reasonable memory consumption
 to make up the loss of deduplication opportunities due to the cross-VM popularity constraint.

%Fingerprint lookup within a VM does not require a signficant  amount of memory resource.

We start with the standard version-based detection~\cite{Clements2009,Vrable2009}
to identify changed content with dirty bits in a coarse grain segment level.
%In our implementation 
%the segment size is 2MB
%and the device driver is extended to support tracking changed segments using a dirty bitmap. 
The reason to choose a coarse grain segment level is that 
since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in 
memory and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. 
%% this method is so widely-used and easy to understand, everyone include Pure Storage has it, I feel no need to explain further.
%{
%For example,
%the VMWare hypervisor has an API to let external backup applications know 
%the changed areas since last backup. 
%The Microsoft SDK provides an API that allows external applications to monitor 
%the VM's I/O traffic and implement such changed block tracking feature.
%}

@@

When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot recipe.  Then recipes of the similar segments are loaded to memory,
which contain chunk fingerprints to be compared.
To control the time cost of search, we set a limit on the number of  similar segment recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For example, assume that  a segment is of size  2MB, 
its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata.
By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
similar segment recipes is 190K, which is tiny compared to other memory requirements.

@@

\item 
\textbf{VM-centric file system block management} --
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
into a file system block.  
In addition to the fact that a distributed file system block is often
configured to be much  larger than a chunk, a number of chunks can be combined together
and compressed further using a standard compression method such as LZO. 
Thus a  backend file system block contains a large number of compressed chunks.
%We manage this accumulation process using a log-structured storage scheme built
%on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
We set the following two constraints in composing chunks for a file system block as follows:
1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
2) A non-PDS file system block is only associated with one VM.

Restricting the association with one VM improves fault isolation when some file blocks are lost during 
storage failure. 
In addition, storing PDS chunks separately from non-PDS chunks
allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%
%One could try to rely on filesystem features to 
If we do not separate the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system and we would have
to add extra replications for {\em all} file blocks in order to   follow the popularity-driven replication idea 
from ~\cite{Reliability06}. That reduces the storage efficiency.
%Then we cannot leverage the file system features to 
%provide extra replication to popular and shared chunks because  
%we have to add extra replication to each file block as long as it contains a popular chunk.

>>>>

% {\it [Need to find a place to put these numbers in: Total number of chunks 
% in 350 snapshots: 1,546,635,485. 
% Total number of chunks after localized dedup: 283,121,924. Total number of unique chunks: 87,692,682.]}
The observation that motivates us to use the PDS
is that for those chunks that appear in different VMs, the top $k$ most popular items
dominate the appearance distribution.  
Figure~\ref{fig:Datazipf} shows the distribution of chunk popularity for a data trace 
from Alibaba with 2500 VMs discussed in Section ~\ref{sect:evaluation}.
We define chunk popularity as the number of unique copies of the chunk in the data-store,
i.e., the number of copies of the chunk after local deduplication.
%the distribution of chunk popularity~\cite{WeiZhangIEEE} 
%based on a production data trace from Alibaba with over 2500 VMs.
The distribution from this figure is Zipf-like. 
Let  $\sigma$ denote as the percentage of unique data chunks belonging to PDS and 
from the evaluation in Section~\ref{sect:evaluation}, we find that
$\sigma$ with about  2\% can deliver a fairly competitive deduplication efficiency.
%$\sigma$ with about  range of 2 to 4\% can deliver a fairly competitive deduplication efficiency.
%For example,
%with top 2\% of the most popular chunks stored in PDS, up-to 40\% of the raw backup 
%data can be eliminated by fingerprint lookup in PDS index.

%when restricting fingerprint comparison within a VM uses
%only a small amount of resource. 
%ehat the local deduplication has removed most of the duplicates.
%There are fewer deduplication opportunities across VMs while the memory and network
%consumption for global comparison is more expensive.
%Thus our approximation is that the global cross-VM fingerprint comparison only searches for the top $k$
%most popular items. 
PDS  can be computed in an offline manner periodically, e.g., on a monthly basis.
%Once the popularity of all data chunks is collected, the system only maintains the top $k$
%most popular chunk fingerprints (called \textbf{PDS index}) in a distributed shared memory.  
%These top chunks are shared among multiple VMs and  since $\sigma$ is relatively small, 
%we can afford to provide extra replicas for these popular chunk data to enhance the fault resilience.
%Compared to a preliminary solution which  uses data popularity~\cite{WeiZhangIEEE}, 
%this paper provides  a more comprehensive scheme with  improved deduplication efficiency and fault tolerance, and
%analytic design guidance. 
% Figure~\ref{fig:Datazipf} illustrates the distribution of chunk popularity based on a data trace from Alibaba with over 2500 VMs.
% The distribution is zipf like and popular chunks are dominating the large portion of data chunks.
% We denote $\sigma$ as the percentage of unique data chunks belonging to PDS and from the evaluation we find that
% $\sigma$ with a range of 1 to 4\% can deliver a fairly competitive deduplication efficiency.
Compared to ~\cite{bottleneck08}, the fingerprint index  size is reduced by $100-\sigma$ percentage
(e.g. 98\% with $\sigma=2\%$)
and the searchable fingerprint space  becomes very small under the popularity constraint.  
The fingerprint-guided distributed mapping in ~\cite{extreme_binning09,Dong2011} narrows
the search scope of each data chunk, but it does not reduce th total amount of searchable fingerprints
used for the entire deduplication. 
%In comparison we only focus on top popular chunks among VMs and this
%significantly reduces the total amount of  searchable fingerprints.

\comments{
We have not adopted the index sampling in \cite{Guo2011} because its extension for
for a distributed architecture is difficult.  To use a distributed memory version of the sampled index, every deduplication 
request may access a remote machine for index lookup and the overall overhead of access latency for all requests
can be significant.
}
\item 
\textbf{VM-specific duplicate search optimization} --
While cross-VM deduplication is simplified, we intend to optimize the VM-specific deduplication 
under a reasonable memory consumption
 to make up the loss of deduplication opportunities due to the cross-VM popularity constraint.
%Fingerprint lookup within a VM does not require a signficant  amount of memory resource.
We start with the standard version-based detection~\cite{Clements2009,Vrable2009}
to identify changed content with dirty bits in a coarse grain segment level.
%In our implementation 
%the segment size is 2MB
%and the device driver is extended to support tracking changed segments using a dirty bitmap. 
The reason to choose a coarse grain segment level is that 
since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in 
memory and cannot afford a small segment size.
It should be noted that dirty bit tracking is supported or can be easily implemented in 
major virtualization solution vendors. 
%% this method is so widely-used and easy to understand, everyone include Pure Storage has it, I feel no need to explain further.
%{
%For example,
%the VMWare hypervisor has an API to let external backup applications know 
%the changed areas since last backup. 
%The Microsoft SDK provides an API that allows external applications to monitor 
%the VM's I/O traffic and implement such changed block tracking feature.
%}

@@

When processing a dirty segment,
its  similar segments can be found easily from the
parent snapshot metadata.  Then metadata of the similar segments is loaded to memory,
which contain chunk fingerprints to be compared.
To control the time cost of search, we set a limit on the number of  similar segment recipes to be fetched. 
% Then,
%given a set of data chunks within a dirty segment,  we compare  these chunk fingerprints
%with those in similar segments.  
For example, assume that  a segment is of size  2MB, 
its segment recipe is roughly 19KB which contains about 500 chunk fingerprints and other chunk metadata.
By limiting at most 10 similar segments to search, the amount of memory for maintaining those 
similar segment recipes is 190K, which is insignificant. 
%compared to other memory requirements.

@@

\item 
\textbf{VM-centric file system block management} --
When a chunk is not detected as a duplicate to any existing chunk, this chunk will be written
into a file system block.  
In addition to the fact that a distributed file system block is often
configured to be much  larger than a chunk, a number of chunks can be combined together
and compressed further using a standard compression method such as LZO. 
Thus a  backend file system block contains a large number of compressed chunks.
%We manage this accumulation process using a log-structured storage scheme built
%on a distributed file system discussed in Section~\ref{sect:architecture}.
%Non-PDS chunks from the same VM are stored in one append store. 
We set the following two constraints in composing chunks for a file system block:
1) Each file system block is either dedicated to non-PDS chunks, or to PDS-chunks.
2) A non-PDS file system block is only associated with one VM.

Restricting the association with one VM improves fault isolation when some file blocks are lost during 
storage failures. 
In addition, storing PDS chunks separately from non-PDS chunks
allows special replication handling for those popular shared data. 
%%% talk something about snapshot store advantage here? %%%
%One could try to rely on filesystem features to 
If we do not separate the
popular chunks from the less-popular, the popular chunks are dispersed across
all of the filesystem blocks in the storage system and we would have
to add extra replications for {\em all} file blocks in order to   follow the popularity-driven replication idea 
from ~\cite{Reliability06}. That reduces the storage efficiency.
%Then we cannot leverage the file system features to 
%provide extra replication to popular and shared chunks because  
%we have to add extra replication to each file block as long as it contains a popular chunk.
